Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Title case
Authors and emails

\title{Constructing Sailing Match Race Schedules: Round Robin Pairing Lists}
\titlerunning{Match Race Scheduling}
%\toctitle{}
\author{Ciaran McCreesh, Craig MacDonald, Alice Miller and Patrick Prosser}
\authorrunning{McCreesh, MacDonald, Miller and Prosser}
\tocauthor{Patrick Prosser}
\institute{School of Computing Science, University of Glasgow, fname.sname@glasgow.ac.uk}
\maketitle

>>>>

\title{Constructing Sailing Match Race Schedules: Round Robin Pairing Lists}
\titlerunning{Match Race Scheduling}
%\toctitle{}
\author{Patrick Prosser \and Ciaran McCreesh\thanks{This work was supported by
the Engineering and Physical Sciences Research Council [grant number
EP/K503058/1]}\and Craig MacDonald \and Alice Miller}
\institute{University of Glasgow, Glasgow, Scotland \\ \email{patrick.prosser@glasgow.ac.uk}}
\authorrunning{Prosser, McCreesh, MacDonald, Miller}
\tocauthor{Patrick Prosser}
\maketitle
